---
title: "rspake1_assignment2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## assignment prompt

prompt:

The Weigelt Corporation has three branch plants with excess production capacity. Fortunately, the corporation has a new product ready to begin production, and all three plants have this capability, so some of the excess capacity can be used in this way. This product can be made in three sizes--large, medium, and small--that yield a net unit profit of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per day of this product, respectively, regardless of the size or combination of sizes involved.The amount of available in-process storage space also imposes a limitation on the production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet, respectively, of in-process storage space available for a day's production of this product. Each unit of the large, medium, and small sizes produced per day requires 20, 15, and 12 square feet, respectively.Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and small sizes, respectively, would be sold per day.At each plant, some employees will need to be laid off unless most of the plant’s excess production capacity can be used to produce the new product. To avoid layoffs if possible, management has decided that the plants should use the same percentage of their excess capacity to produce the new product.Management wishes to know how much of each of the sizes should be produced by each of the plants to maximize profit.Solve the problem using lpsolve, or any other equivalent library in R.

```{r lpsolve}
library(lpSolveAPI)
lprec <- make.lp(0,9)
set.objfn(lprec, c(420,360,300,420,360,300,420,360,300))
lp.control(lprec,sense='max')
add.constraint(lprec, c(1,1,1,0,0,0,0,0,0), "<=", 750)
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0), "<=", 900)
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1), "<=", 450)
add.constraint(lprec, c(20,15,12,0,0,0,0,0,0), "<=", 13000)
add.constraint(lprec, c(0,0,0,20,15,12,0,0,0), "<=", 12000)
add.constraint(lprec, c(0,0,0,0,0,0,20,15,12), "<=", 5000)
add.constraint(lprec, c(1,0,0,1,0,0,1,0,0), "<=", 900)
add.constraint(lprec, c(0,1,0,0,1,0,0,1,0), "<=", 1200)
add.constraint(lprec, c(0,0,1,0,0,1,0,0,1), "<=", 750)
add.constraint(lprec, c(900,900,900,-750,-750,-750,0,0,0), "=", 0)
add.constraint(lprec, c(450,450,450,0,0,0,-750,-750,-750), "=", 0)
RowNames <- c("Capacity1", "Capacity2", "Capaticy3", "Square_footage1", "Square_footage2", "Square_footage3", "Sales1", "Sales2", "Sales3", "Same_perc_of_Cpacity1", "Same_perc_of_Cpacity2")
ColNames <- c("Large1", "Medium1", "Small1","Large2", "Medium2", "Small2","Large3", "Medium3", "Small3")
dimnames(lprec) <- list(RowNames, ColNames)
lprec
write.lp(lprec,filename = "Assignment2.lp", type = "lp")
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)

```

## Explanation

The above code is the R representation of the lp model created in assignment 1, and used in assignment 2. 
after calling the lpsolveapi library, the code creates an lp with 9 columns.
The objective function is then established, inidcating the coefficients for each of the nine columns.
The next line sets the model as a maximization.
The next eleven lines add the necessary constraints to the model. Including the two "non-negative" constraints at the bottom.
Next, an object known as RowNames is created, and eleven labels are stored there in the same order as the constraints.
Then an object known as ColNames is created and nine labels are stored there in the same order as the objective function.
The next line merges the RowNames and ColNames objects into the lp model as the respective headers of rows and columns.
The next line is just the lp model, providing a summary of said model in the output.
Next, an lp file is created known as "Assignment2.lp" to be referenced later if desired.
The last lines solve the lp model, then retreive the objective, variables, and constraints of the model which are displayed at the bottom of the outputs.

