---
title: "rspake1_11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Instructions

AP is a shipping service that guarantees overnight delivery of packages in the continental US. 
The company has various hubs at major cities and airports across the country. Packages are 
received at hubs, and then shipped to intermediate hubs or to their final destination. 
 
The manager of the AP hub in Cleveland is concerned about labor costs, and is interested in 
determining the most effective way to schedule workers. The hub operates seven days a week, 
and the number of packages it handles varies from one day to another. 

Package handlers at AP are guaranteed a five-day work week with two consecutive days off. The 
base wage for the handlers is $750 per week. Workers working on Saturday or Sunday receive an 
additional $25 per day. 

The manager wants to keep the total wage expenses as low as possible while ensuring that there 
are sufficient number of workers available each day. Formulate and solve the problem. What was 
the total cost? How many workers are available each day? 
 
Hint: The number of available workers each day can exceed, but can not be below the required 
amount.

```{r Ap staffing}
library(lpSolveAPI)
Ip_staff <- read.lp("C:/Users/rspake1/Desktop/CSV files/Assignments/Quantitative management modeling/AP_staffing.lp")

Ip_staff

solve(Ip_staff)
get.objective(Ip_staff)
get.variables(Ip_staff)
get.constraints(Ip_staff)

```

## Conclusion

Total Cost = $15,182

Daily Staffing:

Sunday = 18
Monday = 27
Tuesday = 28
Wednesday = 36
Thursday = 26
Friday = 26
Saturday = 19


